---
title: "Old Faithful"
format: 
  html:
    code-tools: 
      source: "https://github.com/quarto-dev/quarto-web/tree/main/docs/interactive/shiny/_examples/old-faithful/shiny-old-faithful.qmd"
server: shiny
---
<!--

2023-10-10	WORKING

USAGE:    quarto serve old-faithful.qmd <CR>   
THEN open browser to <http://127.0.0.1:PORT> Port will display in terminal

REF: 	https://github.com/quarto-dev/quarto-web/blob/main/docs/interactive/shiny/_examples/old-faithful/shiny-old-faithful.qmd

-->

Data on eruptions of the Old Faithful geyser in Yellowstone National Park,
Wyoming, USA. The data was collected continuously from August 1st until
August 15th, 1985.

```{r}
sliderInput("bins", "Number of bins:", min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

The data consists of 299 pairs of measurements, referring to the time interval
between the starts of successive eruptions and the duration of the subsequent
eruption.

Click the **Code** button above to see the source code for this example.

```{r}
#| context: server
output$distPlot <- renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```
